PANCHANGE_analysis

### 2020-09-07 PANCHANGE_analysis.Rmd
Rough counts added for frequencies to be included in presentation.

>>>>

```{r psychiatric disorders frequencies}
#Ppts with least one psychiatric disorder
dat %>%
  count(disorders_total_count >= 1)

#Ppts with anxiety OR depressive disorder
dat %>% 
  count(anxiety_disorders_numeric == 1 | depressive_disorders == 1)

#Ppts with anxiety & depression
dat %>% 
  count(depression_and_anxiety_numeric == 1)
```
